---
title: "Assignment 3 - Machine learning"
author: "Hanish Bhogadi"
date: "3/6/2022"
output:
  pdf_document: default
  html_document: default
---

```{r}
UB <- read.csv("C:/Users/Hanish Bhogadi/Documents/64060_hbhogadi/Assignment_3/UniversalBank.csv")
View(UB)
summary(UB)
library(caret)
library(ISLR)
library(dplyr)
library(class)
library(e1071)
df = UB

#coverting variables
UB$Personal.Loan <- factor(UB$Personal.Loan)
UB$Online <- factor(UB$Online)
UB$CreditCard <- factor(UB$CreditCard)

#Task 1
set.seed(64060)
Train_index <- createDataPartition(df$Personal.Loan, p = 0.6, list = FALSE)
train.df = df[Train_index,]
validation.df = df[-Train_index,]
mytable <- xtabs(~ CreditCard + Online + Personal.Loan, data = train.df)
ftable(mytable)
```

```{r}
#Task 2
#The probability of loan acceptance (Loan = 1) conditional on having a bank
#credit card (CC = 1) and being an active user of online banking services
#(Online = 1)
#Probability of loan acceptance given having a bank credit card and user
Probability = (50/(50+477))
Probability
```

```{r}
#Task 3
table(Personal.Loan = train.df$Personal.Loan, Online = train.df$Online)
table(Personal.Loan = train.df$Personal.Loan, CreditCard = train.df$CreditCard)
table(Personal.Loan = train.df$Personal.Loan)
```

```{r}
#Task 4
#i. P(CC = 1 | Loan = 1) (the proportion of #credit card holders among the loan
#acceptors)
Probability1 <- 85/(85+200)
Probability1

#ii. P(Online = 1 | Loan = 1)
Probability2 <- 174/(111+174)
Probability2

#iii. P(Loan = 1) (the proportion of loan acceptors)
Probability3 <- 285/(285+2715)
Probability3

#iv. P(CC = 1 | Loan = 0)
Probability4 <- 784/(1931+784)
Probability4


#v. P(Online = 1 | Loan = 0)
Probability5 <- 1621/(1621+1094)
Probability5

#vi. P(Loan = 0)
Probability6 <- 2715/(2715+285)
Probability6



```
```{r}
#Task 5
#Use the quantities computed above to compute the naive Ba1 probability
#P(Loan = 1 | CC = 1, Online = 1).
#Let a =
Task5Probablity <- (Probability1*Probability2*Probability3)/((Probability1*Probability2*Probability3)+(Probability4*Probability5*Probability6))
Task5Probablity
```

#Task 6
#Compare this value with the one obtained from the pivot table in (B). Which is
#a more accurate estimate?
#The value derived in 2 was 0.09487666 and in the Task 5 is 0.09980052 are very similar. The only #difference between the exact method and the naive-baise
#method is the exact method would need the the exact same independent variable #classifications to predict, whereas the #naive bayes method does not. We can
#say that the value derived from the Task 2 is more #accurate as we have taken
#the exact values from the pivot table.

#Task 7
#Run naive Bayes on the data. Examine the model output on training data, and
#find the entry that corresponds to P(Loan = 1 | CC = 1, Online = 1).
#Compare this to the number you obtained in (E).
nb.model<-naiveBayes (Personal.Loan~ Online +CreditCard, data=train.df)
To_Predict=data.frame(Online= 1, CreditCard= 1)
predict(nb.model,To_Predict,type='raw')

#The value derived from Task 7 is 0.1013226 and the value derived from the task 5 is 0.09980052. The output #is exactlty same that we received in Task 5 . There is only a minute difference because of the rounding. #The difference will not effect the rank order of the output
